WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-07-18 article/Article.tex
add itk.pipeline doc
darcs-hash:20060718142102-2fc9d-9d8b057800ece96a058abdbfa5b422bd781e5baa.gz

>>>>

  \item \verb$itk.pipeline$ class let the developer easily create
a custom pipeline which can then be manipulated as a pure ITK filter.
It provide several methods:
\begin{itemize}
  \item \verb$__init__( self, input=None )$ is the constructor of the pipeline.
The input of the pipeline can be passed as parameter.

  \item \verb$connect( self, filter )$ connect a new filter to the pipeline.
The output of the last filter in the pipeline will be set as the input of the filter
passed as parameter, and the filter passed as parameter will be added to the filter
list.

  \item \verb$append( self, filter )$ add a filter to the pipeline's filters list,
but don't connect it. The connection must be done by the user. This method is likely
to be used with filters with several inputs.

  \item \verb$clear( self )$  clear the filter list.

  \item \verb$GetOutput( self )$ return the output of the last filter in the pipeline.
If another output is needed, use \verb$pipeline[-1].GetAnotherOutput()$ instead of
this method, or subclass pipeline to implement another \verb$GetOutput()$ method.

  \item \verb$SetInput( self, input )$ set the input of the first filter in the
pipeline. If another input is needed, use \verb$pipeline[0].SetAnotherIntput()$ instead of
this method, or subclass pipeline to implement another \verb$SetIntput()$ method.

  \item \verb$GetInput( self )$ return the input of the last filter in the pipeline.
If another input is needed, use \verb$pipeline[0].GetAnotherInput()$ instead of
this method, or subclass pipeline to implement another \verb$GetInput()$ method.

  \item \verb$Update( self )$ update the pipeline by calling \verb$Update()$ method
on the last filter in the pipeline.

  \item \verb$__getitem__( self, i )$ and \verb$__len__( self )$ provide common
python list manipulation interface to the pipeline object.

Example:
ITK current implementation of morphological dilation, erosion, opening and closing
can be very inefficient with large structuring elements. Also, WrapITK only give
access to ball structuring element. The following class illustrate the use of
\verb$itk.pipeline$ class to implement a efficient opening in 3 dimensions with
a box structuring element. We here take advantage of structuring element decomposition:
a dilation (or erosion) by a box can be more efficiently computed by perfoming
3 dilations (or erosion) with line structuring element oriented on each dimension.
The \verb$itk.pipeline$ encapsulate the 6 filters needed to perform the efficient
opening, and take care of setting the structuring element for all the internal
filters in the \verb$SetKernel(self, x,y,z)$, according to the size wanted by the
user.

\begin{verbatim}
class mkOpeningPipe (itk.pipeline):
  def __init__(self, Input, x=1, y=1, z=1):
    im = itk.image(Input)
    itk.pipeline.__init__(self, im)
    KernelType = itk.class_(itk.strel(3, 0))
    InType = itk.class_(im)
    self.connect(itk.GrayscaleErodeImageFilter[InType, InType, KernelType].New())
    self.connect(itk.GrayscaleErodeImageFilter[InType, InType, KernelType].New())
    self.connect(itk.GrayscaleErodeImageFilter[InType, InType, KernelType].New())
    self.connect(itk.GrayscaleDilateImageFilter[InType, InType, KernelType].New())
    self.connect(itk.GrayscaleDilateImageFilter[InType, InType, KernelType].New())
    self.connect(itk.GrayscaleDilateImageFilter[InType, InType, KernelType].New())
    self.SetKernel(x,y,z)

  def SetKernel(self, x,y,z):
    self[0].SetKernel(itk.strel(3, (x,0,0)))
    self[1].SetKernel(itk.strel(3, (0,y,0)))
    self[2].SetKernel(itk.strel(3, (0,0,z)))
    self[3].SetKernel(itk.strel(3, (x,0,0)))
    self[4].SetKernel(itk.strel(3, (0,y,0)))
    self[5].SetKernel(itk.strel(3, (0,0,z)))
\end{verbatim}

The \verb$mkOpeningPipe$ object can be used as a standard ITK filter:

\begin{verbatim}
reader = itk.ImageFileReader.IUC3.New(FileName='image.tif')
opening = mkOpeningPipe(reader)
ws = itk.MorphologicalWatershedImageFilter.IUC3IUC3.New(opening)
itk.write(ws, "result.tif")
\end{verbatim}
